---
name: Luis Fernando Delgado Muñoz
qualifications: Agroindustrial Engineer, MSc
position: "Data scientist - Professor"
address: "Cali, Colombia"
# profilepic: "./img/Luis Fernando.png"
phone: +57 318 834 0741
# www: https://alliancebioversityciat.org/who-we-are/luis-fernando-delgado
email: "lfdelgadom@unal.edu.co"
#twitter: lfdelgadom
github: lfdelgadom
linkedin: lfdelgadom
orcid: "0000-0002-5443-4678"
# googlescholar: "E7dY4foAAAAJ"
aboutme: "I am an MSc. Agro-Industrial Engineer with expertise in data handling and analysis in agronomy. My experience spans roles as a data scientist in cassava breeding at Alliance of Bioversity and CIAT, and as a professor. I combine data-driven approaches with agricultural studies, proficient in R, Python, command line, and GIT/GitHub. Skilled in managing large datasets, developing statistical models, and effective communication. My commitment to data science in agriculture is underscored by my dedication to teaching and empowering the next generation of data-savvy professionals."
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)
library(vitae)
library(kableExtra)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}
# appointments <- read_csv(here("data", "appointments.csv"))
# education <- read_csv(here("data", "education.csv"))
# research <- read_csv(here("data", "research_experience.csv"))
# teaching <- read_csv(here("data", "teaching_supervision.csv"))
# awards <- read_csv(here("data", "awards.csv"))
# leadership <- read_csv(here("data", "leadership.csv"))
# presentations <- read_csv(here("data", "presentations.csv"))
# training <- read_csv(here("data", "training.csv"))
# skills <- read_csv(here("data", "skills_table.csv"))
# tools <- read_csv(here("data", "digital_tools.csv"))

readExcelSheets(here::here("data", "cv_data.xlsx"))
```

```{r eval=FALSE, include=FALSE}
# To update CV on my website, run the following code in the console:
# rmarkdown::render("cv-vitae/cv-vitae.Rmd", output_file = "~/Documents/SR/website-apero/static/files/cv-vitae.pdf")
```

# Current Appointments

```{r}
appointments %>% 
  detailed_entries(what = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Education

```{r}
education %>% 
  detailed_entries(what = degree, 
                   when = year, 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = FALSE)
```

# Research Experience

```{r}
research %>%
  detailed_entries(what = role,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

<!-- \newpage -->

# Teaching and Supervision

```{r}
teaching %>%
  detailed_entries(what = institution,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

```{r eval=FALSE, include=FALSE}
# leadership %>%
#   detailed_entries(what = glue::glue("\\textbf{<role>}: <institution> (<where>)",
#                                      .open = "<", .close = ">"),
#                    why = details,
#                    when = dates, #glue::glue("{start_date}--{end_date}"), 
#                    .protect = FALSE)

# leadership <- leadership %>% mutate(details = replace_na(details, " "))

# leadership %>%
#   brief_entries(what = glue::glue("\\textbf{<role>} \\textit{(<institution>)}. <details>", .open = "<", .close = ">"),
#                 when = dates, .protect = FALSE)
```

# Additional training and professional development

```{r}
training %>%
  brief_entries(what = glue::glue("\\textbf{<training>} (<institution>)", .open = "<", .close = ">"),
                when = year, 
                .protect = FALSE)
```

# Skills

```{r}
# skills <- read_csv(here("data", "skills.csv"))
# skills %>%
#   detailed_entries(with = type,
#                    why = skill)
# 
skills %>%
  kable(booktabs = TRUE, format = "latex") %>%
  kable_styling(full_width = F, font_size = 8, latex_options = "hold_position") %>%
  row_spec(0, bold = T)
```

```{r eval=FALSE, include=FALSE}
# awards %>% 
#   detailed_entries(what = institution,
#                    when = year,
#                    with = award,
#                    why = details)

# awards %>%
#   brief_entries(glue::glue("\\textbf{<award>} (<institution>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

```{r}
# did not like this format so will add manually for now
# bibliography_entries(here("data", "papers.bib")) 
```

```{r eval=FALSE, include=FALSE}
# tools %>%
#   detailed_entries(what = authors,
#                    when = year,
#                    with = tool,
#                    why = details,
#                    .protect = FALSE)

# tools %>% 
#   brief_entries(glue::glue("\\textbf{<tool>}, (Authors: <authors>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

<!-- \newpage -->

# Selected presentations

```{r}
presentations <- presentations %>% filter(include == "yes")

presentations %>%
  brief_entries(glue::glue("\\textbf{<topic>}, <where>", .open = "<", .close = ">"),
                paste0(year, "\\newline~\\newline"),
                .protect = FALSE)
```

# Publications

\footnotesize

```{r}
# did not like this format so will add manually for now
# bibliography_entries(here("data", "papers.bib")) 
```

\setlength{\leftskip}{0cm}

**2023**

\setlength{\leftskip}{1cm}

Meghar, K., Tran, T., **Delgado, L.F.**, Ospina, M.A., Moreno, J.L., Luna, J., Londono, L.F., Dufour, D., Davrieux, F.(2023). *Hyperspectral imaging for the determinationof relevant cooking quality traits of boiledcassava*.J Sci Food Agric. <https://doi.org/10.1002/jsfa.12654>

Mestres C., Taylor M., McDougall G., Arufe S., Tran T., Nuwamanya E., Dufour D., Nakitto M., Meghar K., Rinaldo D., Ollier L., Domingo R., Moreno J.L., **Delgado Muñoz, L.F.**, Kouassi H.A., Diby N'Nan Afoué S., Mbeguie-A-Mbeguie D., Akissoe N., Adinsi L., Rolland-Sabate A. (2023). *Contrasting effects of polysaccharide components on the cooking properties of Roots, Tubers and Bananas (RTBs)*.J Sci Food Agric. <https://doi.org/10.1002/jsfa.12914>

Ayetigbo, O., Arufe, S., Kouassi, A., Adinsi, L., Adesokan, M., Escobar, A., **Delgado, L. F.**, Tanimola, A., Oroniran, O., Kendine Vepowo, C., Nakitto, M., Khakasa, E., Chijioke, U., Nowakunda, K., Ngoh Newilah, G., Otegbayo, B., Akissoe, N., Lechaudel, M., Tran, T., ... Dufour, D. (2023). **Review of instrumental texture measurements as phenotypic tool to assess textural diversity of root, tuber and banana food products.** Journal of the Science of Food and Agriculture, jsfa.13072. <https://doi.org/10.1002/jsfa.13072>

\setlength{\leftskip}{0cm}

**2022**

\setlength{\leftskip}{1cm}

Vásquez Amariles, H., Saavedra Ospina, R., Guerrero Cobos, D., Marín Beitia, E., Escobar Hernández, G., Cifuentes Gutiérrez, C.A., Caicedo Vallejo, A.M., Mosquera Escobar, L.E., **Delgado Muñoz, L.F.** (2022). **Opciones tecnológicas para mejorar las prácticas agronómicas en el cultivo de aguacate Hass en zona de ladera, Colombia: Parcela demostrativa de aguacate Hass establecida en zona de ladera, Colombia.** Bogotá: Universidad Nacional de Colombia. <https://repositorio.unal.edu.co/handle/unal/82746>

Vásquez Amariles, H., Guerrero Cobos, D., Castro López, V., Gutiérrez Pineda O., Gutiérrez Pineda Caicedo Vallejo, A.M., Mosquera Escobar, L.E., **Delgado Muñoz, L.F.** (2022). **Opciones tecnológicas para mejorar las prácticas agronómicas en el cultivo de mora en zona de ladera, Colombia: Parcela demostrativa de mora establecida en zona de ladera.** Universidad Nacional de Colombia. <https://repositorio.unal.edu.co/handle/unal/82722>

# References

-   Xiaofei Zhang, PhD. Global cassava breeder CIAT. Phone: +1 (612)802-8711 Email: [Xiaofei.Zhang\@cgiar.org](mailto:Xiaofei.Zhang@cgiar.org){.email}

-   Danilo Moreta, PhD. Postdoctoral researcher Cassava program CIAT. Phone: +57 321 2531441 Email: [d.moreta\@cgiar.org](mailto:d.moreta@cgiar.org){.email}
