%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Luis Fernando Delgado Muñoz}{}

\position{Data scientist - Lecturer}
\address{Cali, Colombia}

\mobile{+57 318 834 0741}
\email{\href{mailto:lfdelgadom@unal.edu.co}{\nolinkurl{lfdelgadom@unal.edu.co}}}
\orcid{0000-0002-5443-4678}
\github{lfdelgadom}
\linkedin{lfdelgadom}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I am an MSc. Agro-Industrial Engineer with expertise in data
handling and analysis in agronomy. My experience spans roles as a data
scientist in cassava breeding at Alliance of Bioversity and CIAT, and as
a professor. I combine data-driven approaches with agricultural studies,
proficient in R, Python, command line, and GIT/GitHub. Skilled in
managing large datasets, developing statistical models, and effective
communication. My commitment to data science in agriculture is
underscored by my dedication to teaching and empowering the next
generation of professionals.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {March 2024}
    {Luis Fernando Delgado Muñoz~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{current-appointments}{%
\section{Current Appointments}\label{current-appointments}}

\begin{cventries}
    \cventry{Data scientist - Cassava program. \href{https://alliancebioversityciat.org/who-we-are/luis-fernando-delgado}{\faExternalLink}}{The Alliance Bioversity International and CIAT}{Palmira, Colombia}{Jul 2022--Present}{}\vspace{-4.0mm}
    \cventry{Lecturer, Engineering faculty, \href{https://www.uceva.edu.co/facultad-de-ingenieria/ingenieria-agropecuaria/}{Agropecuary Engineering program \faExternalLink}}{Unidad Central del Valle.}{Tulúa, Colombia}{Aug 2020--Present}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Agroindustrial Engineering}{Universidad Nacional de Colombia Sede Palmira}{Palmira, Colombia}{2015}{}\vspace{-4.0mm}
    \cventry{MSc. Agricultural Sciences}{Universidad Nacional de Colombia Sede Palmira}{Palmira, Colombia}{2019}{\begin{cvitems}
\item Best master Thesis Award Laureate (2019)
\item \textbf{Thesis}: Characterization of Tabasco and Cayenne chile oleoresins under different nitrogen and soil moisture levels. \href{https://repositorio.unal.edu.co/handle/unal/76744}{\faExternalLink}
\end{cvitems}}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\begin{cventries}
    \cventry{Data scientist,  Cassava program}{The Alliance Bioversity International and CIAT}{Palmira, Colombia}{Jul 2022--Present}{\begin{cvitems}
\item Analize data of historical trials in the past 50 years from the Cassava Program.
\item Calculate the genetic gain for all breeding populations of the cassava program.
\item Develop standard analysis pipelines for advance yield trials, early trials, post-harvest quality data, and genotypic data.
\item Submit report on genetic gain in cassava, beans, rice and forages to Excellence in Breeding through CGIAR Genetic Innovation Initiatives.
\item Support the breeding team through the full breeding cycle from design, and data analysis to publication.
\item Management and storage of data analysis in the Cassava2050 gitHub account \href{https://github.com/Cassava2050}{See GitHub \faExternalLink}
\item Collaborate with the OneCG Biometrics Group to develop data analysis tools.
\end{cvitems}}
    \cventry{Research Assistant Fellow, Quality postharvest lab, Cassava program}{The Alliance Bioversity International and CIAT - Manpower group}{Palmira, Colombia}{Dec 2020--Jun 2022}{\begin{cvitems}
\item Provide support for raw root processing, textural analysis, and optimal cooking time evaluations of breeding populations of the cassava program.
\item Training of panelists on the sensory attributes of cooked cassava roots and establishment of the first sensory panel of the cassava breeding program.
\item Provide support for data cleaning, curation, and statistical analysis of RTB Foods project data.
\end{cvitems}}
    \cventry{Statistical data analyst}{Universidad Nacional de Colombia Sede Palmira}{Palmira, Colombia}{Dec 2021--Feb 2022}{\begin{cvitems}
\item Statistical analysis of Hass avocado demonstration plots in the municipality of Roldanillo.
\item Statistical analysis of blackberry crop demonstration plots in the municipality of Pradera
\end{cvitems}}
\end{cventries}

\newpage

\hypertarget{teaching-and-supervision}{%
\section{Teaching and Supervision}\label{teaching-and-supervision}}

\begin{cventries}
    \cventry{Universidad Unidad Central del Valle Cauca}{Lecturer}{Tulúa, Colombia}{Aug 2020--Present}{\begin{cvitems}
\item Provide teaching at the Faculty of Engineering, Agricultural Engineering Course, including subjects: Research Tools I and Experimental Design with R Programming.
\end{cvitems}}
    \cventry{International Atomic Energy agency}{Guest lecturer}{Faisalabad, Pakistan}{Nov 2023--Nov 2023}{\begin{cvitems}
\item Invited by the IAEA to train participants from Pakistan, South East Asia and the Pacific Islands in experimental design and phenotypic data analysis at the Regional Training Course in Experimental Design and Data Analysis of Mutant Populations.
\end{cvitems}}
    \cventry{Universidad Nacional de Colombia Sede Palmira}{Lecturer}{Palmira, Colombia}{Feb 2020--Jul 2023}{\begin{cvitems}
\item Provide teaching at the Faculty of Engineering and Administration, PhD program: Food Science and Technology, courses include: Analysis and Experimental Design
\end{cvitems}}
\end{cventries}

\hypertarget{additional-training-and-professional-development}{%
\section{Additional training and professional
development}\label{additional-training-and-professional-development}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Data Bootcamp for Genomic Prediction in Plant Breeding} (University of Minnesota)}{}{2023}
    \cvhonor{}{\textbf{Genomewide Markers in plant breeding} (University of Minnesota)}{}{2023}
    \cvhonor{}{\textbf{A Short Introduction to ASReml-R} (VSN international)}{}{2023}
    \cvhonor{}{\textbf{Genomic Prediction and Selection} (NextGen Cassava Breeding Project)}{}{2022}
    \cvhonor{}{\textbf{Phenotypic modelling of multi-enviroment trials} (Wageningen University)}{}{2021}
    \cvhonor{}{\textbf{Design of experiments for optimization} (Udemy)}{}{2021}
\end{cvhonors}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\begin{table}[!h]
\centering\begingroup\fontsize{8}{10}\selectfont

\begin{tabular}{lll}
\toprule
\textbf{Analytical} & \textbf{Programming} & \textbf{Software/Tools}\\
\midrule
Phenotype database curation/management & R (advanced) & Git\\
Univariate/multivariate data analysis & Python (intermediate) & GitHub\\
Linear mixed models & Asreml & Shiny\\
Reproducible research & Linux (intermediate) & LaTeX\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\hypertarget{selected-presentations}{%
\section{Selected presentations}\label{selected-presentations}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Data analysis pipeline in cassava breeding, Cali, Colombia}, Presented at the Alliance Science Seminar Series \href{https://youtu.be/keIB6qb80Wk?si=-cva6XBWGnyq6vga/}{See recording \faExternalLink}}{}{2023\newline~\newline}
    \cvhonor{}{\textbf{Enhancing the Nutritional Value and Agronomic Performance of Tuber Crops: Making Genetic Gains in Biofortified Cassava Over a Decade at CIAT, 
Ben Guerir, Morocco.}, Poster presentation at The African Plant Breeders Association Conference
3rd Edition \href{https://hdl.handle.net/10568/132698}{See poster \faExternalLink}}{}{2023\newline~\newline}
    \cvhonor{}{\textbf{Adding value and minimizing losses: Post-harvest deterioration in Cassava, Cali, Colombia}, Presented at the Cassava retreat 2023 \href{https://hdl.handle.net/10568/131658}{See slides \faExternalLink}}{}{2023\newline~\newline}
    \cvhonor{}{\textbf{Mattson cooker improves the accuracy of cassava cooking time evaluation​, Nairobi, Kenya}, Poster presentation at 19th International Triennial Symposium of the International Society for Tropical Root Crops (ISTRC)}{}{2022\newline~\newline}
    \cvhonor{}{\textbf{International sustainable agriculture training course}, Presented at Universidad Central del Valle del Cauca for undergraduated students from Colombia and Guatemala}{}{2022\newline~\newline}
    \cvhonor{}{\textbf{Assessing Boiled Cassava Cooking time: Mattson cooker replaces subjective fork detection method on boiled cassava roots}, Presented at the RTBfoods Webinar \href{https://youtu.be/lfdarLZkFto?si=MR3D2FROhJE2NeG6}{See recording \faExternalLink}}{}{2022\newline~\newline}
    \cvhonor{}{\textbf{Agro-industrial trends in the uses of capsicum species}, Invited to speak at the 1 st Ibero-American Congress on Agrifood Sciences, SENA}{}{2017\newline~\newline}
\end{cvhonors}

\newpage

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\footnotesize

\setlength{\leftskip}{0cm}

\textbf{2024}

\setlength{\leftskip}{1cm}

Iragaba, P., Adinsi, L., \textbf{Delgado, L. F.}, Nanyonjo, A. R.,
Nuwamanya, E., Wembabazi, E., Kanaabi, M., Honfozo, L., Hotegni, F.,
Djibril-Moussa, I., Londoño, L. F., Bugaud, C., Dufour, D., Kawuki, R.
S., Akissoé, N., \& Tran, T.(2024). \emph{Definition of sensory and
instrumental thresholds of acceptability for selection of cassava
genotypes with improved boiling properties}.J Sci Food Agric.
\url{https://doi.org/10.1002/jsfa.13363}

\setlength{\leftskip}{0cm}

\textbf{2023}

\setlength{\leftskip}{1cm}

Meghar, K., Tran, T., \textbf{Delgado, L.F.}, Ospina, M.A., Moreno,
J.L., Luna, J., Londono, L.F., Dufour, D., Davrieux, F.(2023).
\emph{Hyperspectral imaging for the determination of relevant cooking
quality traits of boiledcassava}.J Sci Food Agric.
\url{https://doi.org/10.1002/jsfa.12654}

Mestres C., Taylor M., McDougall G., Arufe S., Tran T., Nuwamanya E.,
Dufour D., Nakitto M., Meghar K., Rinaldo D., Ollier L., Domingo R.,
Moreno J.L., \textbf{Delgado Muñoz, L.F.}, Kouassi H.A., Diby N'Nan
Afoué S., Mbeguie-A-Mbeguie D., Akissoe N., Adinsi L., Rolland-Sabate A.
(2023). \emph{Contrasting effects of polysaccharide components on the
cooking properties of Roots, Tubers and Bananas (RTBs)}.J Sci Food
Agric. \url{https://doi.org/10.1002/jsfa.12914}

Ayetigbo, O., Arufe, S., Kouassi, A., Adinsi, L., Adesokan, M., Escobar,
A., \textbf{Delgado, L. F.}, Tanimola, A., Oroniran, O., Kendine Vepowo,
C., Nakitto, M., Khakasa, E., Chijioke, U., Nowakunda, K., Ngoh Newilah,
G., Otegbayo, B., Akissoe, N., Lechaudel, M., Tran, T., \ldots{} Dufour,
D. (2023). \textbf{Review of instrumental texture measurements as
phenotypic tool to assess textural diversity of root, tuber and banana
food products.} J Sci Food Agric.
\url{https://doi.org/10.1002/jsfa.13072}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{itemize}
\item
  Xiaofei Zhang, PhD. Assistant Professor. Phone: +1 (612)802-8711
  Email:
  \href{mailto:xfczhang@ucdavis.edu}{\nolinkurl{xfczhang@ucdavis.edu}}
\item
  Danilo Moreta, PhD. Postdoctoral researcher Cassava program CIAT.
  Phone: +57 321 2531441 Email:
  \href{mailto:d.moreta@cgiar.org}{\nolinkurl{d.moreta@cgiar.org}}
\end{itemize}


\label{LastPage}~
\end{document}
