---
name: Luis Fernando Delgado Muñoz
qualifications: Agroindustrial Engeneer, MSc
position: "Statistical data analyst"
address: "Cali, Colombia"
profilepic: "./img/Luis Fernando.png"
phone: +57 318 834 0741
# www: shaziaruybal.com
email: "lfdelgadom@unal.edu.co"
twitter: lfdelgadom
github: lfdelgadom
linkedin: lfdelgadom
# orcid: "0000-0002-0495-179X"
# googlescholar: "E7dY4foAAAAJ"
aboutme: "Agro-industrial engineer with expertise in data handle and data analytics from field and quality postharvest trials of cassava breeding populations. I'm interested in combining these approaches to breeding population-based studies of economical traits, particularly dry matter, yield, diseases resistant and quality postharvest traits. My work has involved international collaborations in France and the Americas, and spans harvesting breeding populations, to evaluation and characterization of quality traits in the lab, to the downstream analytics using advanced approaches and digital tools. I am an avid `R` user for data processing, analytics, modelling,visualization, communication and reports."
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)
library(vitae)
library(kableExtra)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}
# appointments <- read_csv(here("data", "appointments.csv"))
# education <- read_csv(here("data", "education.csv"))
# research <- read_csv(here("data", "research_experience.csv"))
# teaching <- read_csv(here("data", "teaching_supervision.csv"))
# awards <- read_csv(here("data", "awards.csv"))
# leadership <- read_csv(here("data", "leadership.csv"))
# presentations <- read_csv(here("data", "presentations.csv"))
# training <- read_csv(here("data", "training.csv"))
# skills <- read_csv(here("data", "skills_table.csv"))
# tools <- read_csv(here("data", "digital_tools.csv"))

readExcelSheets(here::here("data", "cv_data.xlsx"))
```

```{r eval=FALSE, include=FALSE}
# To update CV on my website, run the following code in the console:
# rmarkdown::render("cv-vitae/cv-vitae.Rmd", output_file = "~/Documents/SR/website-apero/static/files/cv-vitae.pdf")
```

# Current Appointments

```{r}
appointments %>% 
  detailed_entries(what = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Education

```{r}
education %>% 
  detailed_entries(what = degree, 
                   when = year, 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = FALSE)
```

# Research Experience

```{r}
research %>%
  detailed_entries(what = role,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

<!-- \newpage -->
\newpage

# Teaching and Supervision

```{r}
teaching %>%
  detailed_entries(what = institution,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```


```{r eval=FALSE, include=FALSE}
# leadership %>%
#   detailed_entries(what = glue::glue("\\textbf{<role>}: <institution> (<where>)",
#                                      .open = "<", .close = ">"),
#                    why = details,
#                    when = dates, #glue::glue("{start_date}--{end_date}"), 
#                    .protect = FALSE)

# leadership <- leadership %>% mutate(details = replace_na(details, " "))

# leadership %>%
#   brief_entries(what = glue::glue("\\textbf{<role>} \\textit{(<institution>)}. <details>", .open = "<", .close = ">"),
#                 when = dates, .protect = FALSE)
```

# Additional training and professional development

```{r}
training %>%
  brief_entries(what = glue::glue("\\textbf{<training>} (<institution>)", .open = "<", .close = ">"),
                when = year, 
                .protect = FALSE)
```

# Skills

```{r}
# skills <- read_csv(here("data", "skills.csv"))
# skills %>%
#   detailed_entries(with = type,
#                    why = skill)
# 
skills %>%
  kable(booktabs = TRUE, format = "latex") %>%
  kable_styling(full_width = F, font_size = 8, latex_options = "hold_position") %>%
  row_spec(0, bold = T)
```


```{r eval=FALSE, include=FALSE}
# awards %>% 
#   detailed_entries(what = institution,
#                    when = year,
#                    with = award,
#                    why = details)

# awards %>%
#   brief_entries(glue::glue("\\textbf{<award>} (<institution>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

```{r}
# did not like this format so will add manually for now
# bibliography_entries(here("data", "papers.bib")) 
```


```{r eval=FALSE, include=FALSE}
# tools %>%
#   detailed_entries(what = authors,
#                    when = year,
#                    with = tool,
#                    why = details,
#                    .protect = FALSE)

# tools %>% 
#   brief_entries(glue::glue("\\textbf{<tool>}, (Authors: <authors>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

<!-- \newpage -->

# Selected presentations


```{r}
presentations <- presentations %>% filter(include == "yes")

presentations %>%
  brief_entries(glue::glue("\\textbf{<topic>}, <where>", .open = "<", .close = ">"),
                paste0(year, "\\newline~\\newline"),
                .protect = FALSE)
```

# References

- Thierry Tran, PhD. Lead cassava postharvest quality laboratory CIAT. Phone: +4450000 ext: 3063 Email: thierry.Tran@cgiar.org 

- Luis Fernando Londoño, PhD(c), MSc. Senior cassava postharvest quality laboratory coordinator CIAT.
Phone: +4450000 ext: 3063
Celephone: +57 310 4315682
Email: L.Londono@cgiar.org

- Daniel Gerardo Cayón Salinas, PhD. Professor Universidad Nacional de Colombia Sede Palmira.
Phone: +572 2868888 Ext.: 35132-3513
Celephone: +57 315 2489251
Email: dgcayons@unal.edu.co


