---
name: Luis Fernando Delgado Muñoz
qualifications: Agroindustrial Engineer, MSc
position: "Statistical data analyst - Professor"
address: "Cali, Colombia"
# profilepic: "./img/Luis Fernando.png"
phone: +57 318 834 0741
# www: shaziaruybal.com
email: "lfdelgadom@unal.edu.co"
#twitter: lfdelgadom
github: lfdelgadom
linkedin: lfdelgadom
# orcid: "0000-0002-0495-179X"
# googlescholar: "E7dY4foAAAAJ"
aboutme: "I am a dedicated and passionate MSc. Agro-industrial engineer with expertise in data handling, processing, and analytics of agronomic and livestock sciences. My professional journey spans as a Data Analyst in the Cassava Breeding Program at CIAT and a University Professor. I am driven by my commitment to combining data-driven approaches with breeding population-based studies of economical traits in agriculture. As an educator, I focus on empowering students in data handling, processing, analytics, and gaining insights from data, fostering the next generation of data-driven leaders. Proficient in R and Python, I efficiently manipulate and analyze large datasets, develop statistical models, create compelling visualizations, and effectively communicate findings to diverse stakeholders."
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)
library(vitae)
library(kableExtra)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}
# appointments <- read_csv(here("data", "appointments.csv"))
# education <- read_csv(here("data", "education.csv"))
# research <- read_csv(here("data", "research_experience.csv"))
# teaching <- read_csv(here("data", "teaching_supervision.csv"))
# awards <- read_csv(here("data", "awards.csv"))
# leadership <- read_csv(here("data", "leadership.csv"))
# presentations <- read_csv(here("data", "presentations.csv"))
# training <- read_csv(here("data", "training.csv"))
# skills <- read_csv(here("data", "skills_table.csv"))
# tools <- read_csv(here("data", "digital_tools.csv"))

readExcelSheets(here::here("data", "cv_data.xlsx"))
```

```{r eval=FALSE, include=FALSE}
# To update CV on my website, run the following code in the console:
# rmarkdown::render("cv-vitae/cv-vitae.Rmd", output_file = "~/Documents/SR/website-apero/static/files/cv-vitae.pdf")
```

# Current Appointments

```{r}
appointments %>% 
  detailed_entries(what = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Education

```{r}
education %>% 
  detailed_entries(what = degree, 
                   when = year, 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = FALSE)
```

# Research Experience

```{r}
research %>%
  detailed_entries(what = role,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Teaching and Supervision

```{r}
teaching %>%
  detailed_entries(what = institution,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```


```{r eval=FALSE, include=FALSE}
# leadership %>%
#   detailed_entries(what = glue::glue("\\textbf{<role>}: <institution> (<where>)",
#                                      .open = "<", .close = ">"),
#                    why = details,
#                    when = dates, #glue::glue("{start_date}--{end_date}"), 
#                    .protect = FALSE)

# leadership <- leadership %>% mutate(details = replace_na(details, " "))

# leadership %>%
#   brief_entries(what = glue::glue("\\textbf{<role>} \\textit{(<institution>)}. <details>", .open = "<", .close = ">"),
#                 when = dates, .protect = FALSE)
```

# Additional training and professional development

```{r}
training %>%
  brief_entries(what = glue::glue("\\textbf{<training>} (<institution>)", .open = "<", .close = ">"),
                when = year, 
                .protect = FALSE)
```

# Skills

```{r}
# skills <- read_csv(here("data", "skills.csv"))
# skills %>%
#   detailed_entries(with = type,
#                    why = skill)
# 
skills %>%
  kable(booktabs = TRUE, format = "latex") %>%
  kable_styling(full_width = F, font_size = 8, latex_options = "hold_position") %>%
  row_spec(0, bold = T)
```


```{r eval=FALSE, include=FALSE}
# awards %>% 
#   detailed_entries(what = institution,
#                    when = year,
#                    with = award,
#                    why = details)

# awards %>%
#   brief_entries(glue::glue("\\textbf{<award>} (<institution>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

```{r}
# did not like this format so will add manually for now
# bibliography_entries(here("data", "papers.bib")) 
```


```{r eval=FALSE, include=FALSE}
# tools %>%
#   detailed_entries(what = authors,
#                    when = year,
#                    with = tool,
#                    why = details,
#                    .protect = FALSE)

# tools %>% 
#   brief_entries(glue::glue("\\textbf{<tool>}, (Authors: <authors>): <details>", .open = "<", .close = ">"),
#                 paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

<!-- \newpage -->

# Selected presentations


```{r}
presentations <- presentations %>% filter(include == "yes")

presentations %>%
  brief_entries(glue::glue("\\textbf{<topic>}, <where>", .open = "<", .close = ">"),
                paste0(year, "\\newline~\\newline"),
                .protect = FALSE)
```

# Publications
\footnotesize
```{r}
# did not like this format so will add manually for now
# bibliography_entries(here("data", "papers.bib")) 
```


\setlength{\leftskip}{0cm}
**2023**

\setlength{\leftskip}{1cm}
Meghar, K., Tran, T., **Delgado, L.F.**, Ospina, M.A., Moreno, J.L., Luna, J., Londono, L.F., Dufour, D., Davrieux, F.(2022). *Hyperspectral imaging for the determinationof relevant cooking quality traits of boiledcassava*.J Sci Food Agric. https://doi.org/10.1002/jsfa.12654

\setlength{\leftskip}{0cm}
**2022** 

\setlength{\leftskip}{1cm}
Vásquez Amariles, H., Saavedra Ospina, R., Guerrero Cobos, D., Marín Beitia, E., Escobar Hernández, G., Cifuentes Gutiérrez, C.A., Caicedo Vallejo, A.M., Mosquera Escobar, L.E., **Delgado Muñoz, L.F.** (2022). **Opciones tecnológicas para mejorar las prácticas agronómicas en el cultivo de aguacate Hass en zona de ladera, Colombia: Parcela demostrativa de aguacate Hass establecida en zona de ladera, Colombia.** Bogotá: Universidad Nacional de Colombia. https://repositorio.unal.edu.co/handle/unal/82746

Vásquez Amariles, H., Guerrero Cobos, D., Castro López, V., Gutiérrez Pineda O., Gutiérrez Pineda Caicedo Vallejo, A.M., Mosquera Escobar, L.E., **Delgado Muñoz, L.F.**  (2022). **Opciones tecnológicas para mejorar las prácticas agronómicas en el cultivo de mora en zona de ladera, Colombia: Parcela demostrativa de mora establecida en zona de ladera.** Universidad Nacional de Colombia. https://repositorio.unal.edu.co/handle/unal/82722

# References

- Thierry Tran, PhD. Lead cassava postharvest quality laboratory CIAT. Phone: +4450000 ext: 3063 Email: thierry.Tran@cgiar.org 

- Luis Fernando Londoño, PhD(c), MSc. Senior cassava postharvest quality laboratory coordinator CIAT.
Phone: +4450000 ext: 3063
Celephone: +57 310 4315682
Email: L.Londono@cgiar.org

- Daniel Gerardo Cayón Salinas, PhD. Professor Universidad Nacional de Colombia Sede Palmira.
Phone: +572 2868888 Ext.: 35132-3513
Celephone: +57 315 2489251
Email: dgcayons@unal.edu.co


